%!Mode:: "TeX:UTF-8"
%!TEX encoding = UTF-8 Unicode
%!TEX TS-program = xelatex
\documentclass{ctexart}
\newif\ifpreface
\prefacetrue
\input{../../../global/all}
\begin{document}
\large
\setlength{\baselineskip}{1.2em}
\ifpreface
	\input{../../../global/preface}
	\newgeometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
\else
	\newgeometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
	\maketitle
\fi
%from_here_to_type
\begin{problem}
Assume \(V\) is irreducible algebraic set in \(\mathbbm{A}_k^{n}\).
Assume \(\theta:\mathbbm{A}_k^{n} \to \mathbb{P}_k^{n}\) is the imbedding.
Prove that \(\overline{\theta(V)} \subset \mathbb{P}_k^{n}\) is irreducible.
\end{problem}

\begin{solution}
  If not, assume \(\overline{\theta(V)}= W_1 \cup W_2\), where \(W_1,W_2 \subsetneq \theta(V)\) are algebraic set. 
  First we prove \(\overline{\theta(V)} \cap U_0=\theta(V)\), where \(U_0=\{[x_0,\cdots,x_n]:x_0 \neq 0\}\). 
  Obviously \(\theta(V)\subset \overline{\theta(V)} \cap U_0\), so we only need to prove \(\overline{\theta(V)} \cap U_0 \subset \theta(V)\). 
  Consider \(\Phi:k[x_0,\cdots,x_n] \to k[x_1,\cdots,x_n],f(x_0,\cdots,x_n)\mapsto f(1,x_1,\cdots,x_n)\). 
  Then we have for any algebraic set \(W\) in \(\mathbb{P}_k^n\), \(\Phi(\ide(W))=\ide(\theta^{-1}(W\cap U_0))\). 
  Let \(W=\overline{\theta(V)}\), we get \(\ide(\theta^{-1}(W \cap U_0))=\Phi(\ide(W))=\ide(V)\). 
  So \(\theta^{-1}(W \cap U_0) \subset V\). 

  Now consider \(W_1 \cap U_0,W_2 \cap U_0\). Since \(\overline{W_1 \cap U_0}\subset W_1 \subsetneq V=\overline{\theta(V)}\), 
  we get \(W_1 \cap U_0,W_2 \cap U_0 \subsetneq \theta(V)\), so \(V=\theta^{-1}(W_1 \cap U_0) \cup \theta^{-1}(W_2 \cap U_0)\) is reducible, contradiction! 
  So we get \(\overline{(\theta(V))}\) is irreducible. 
\end{solution}
\begin{problem}
  Assume \(k\) is a algebraic closed field, \(f \in k[x_1,\cdots,x_n]\) is irreducible, prove that \(\van(f)\subset \mathbbm{A}_k^{n}\) is irreducible algebraic set. 
\end{problem}
\begin{solution}
  Only need to prove \((f)\) is prime ideal. i.e., \(f \mid gh \to f \mid g \vee f \mid h\). 
  Since \(k[x_1,\cdots,x_n]\) is Unique factorization domain, we get \(f\) is prime element. 
  So it's obvious. 
\end{solution}

\begin{problem}
  Assume \(V\) is irreducible algebraic set in \(\mathbbm{A}_k^{n}\), and \(U \subset V\) is nonempty open set in \(V\). 
  Assume \(f,g \in k(V)\) and \(\forall p \in U,f(p)=g(p)\). Prove that \(f=g\) in \(k(V)\). 
\end{problem}

\begin{solution}
  Assume \(f=\frac{f_1}{f_2},g=\frac{g_1}{g_2}\), where \(f_1,f_2,g_1,g_2 \in k[x_1,\cdots,x_n]\).
  And without loss of generality we assume \(U \subset \dom(f_2),\dom(g_2)\), or we use \(\dom(f_2) \cap \dom(g_2)\) replace \(U\). 
  To prove \(f=g\) in \(k(V)\), we only need to prove \(f_1g_2-f_2g_1=0\). 
  Consider \(h=f_1 g_2 - f_2 g_1 \in k[x_1,\cdots,x_n]\). We have \(U \subset \van(h)\). 
  So \((V\setminus U) \cup \van(h)=V\). Since \(V\) is irreducible, we get \(V\setminus U=V \vee \van(h)=V\). 
  Since \(U \neq \varnothing\), we get \(\van(h)=V\), so \(h=0\) in \(k(V)\).
\end{solution}
\end{document}
