%!Mode:: "TeX:UTF-8"
%!TEX TS-program = xelatex
\documentclass{ctexart}
\newif\ifpreface
\prefacetrue
\input{../../../global/all}
\begin{document}
\large
\setlength{\baselineskip}{1.2em}
\date{北京师范大学数学科学学院}
\ifpreface
	\input{../../../global/preface}
\else
	\maketitle
\fi
\newgeometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
%from_here_to_type
%作业：第一节习题(p3): 2,4; 第二节习题(p6): 3; 第三节习题(p10): 3
\begin{problem}\label{pro:p3.2}
	Prove that \(\forall n \in \mathbb{Z},3 \mid n(n+1)(2n + 1)\).
\end{problem}
\begin{solution}
	If \(n \equiv 0 \mod 3\) then \(3 \mid n\).
	If \(n \equiv 1 \mod 3\) then \(3 \mid 2n+1\).
	So no matter what is \(n \mod 3\), we can obtain \(3 \mid n(n + 1)(2n + 1)\).
\end{solution}

\begin{problem}\label{pro:p3.4}
	Let \(a,b \in \mathbb{Z}\) and \(b \neq 0\). Prove that there exists a pair of \(s,t \in \mathbb{Z}\) such that \(a=sb + t \AND |t|\leq \frac{|b|}{2}\).
	And if \(b\) is odd, then the pair \(s,t\) is unique.
	What if \(b\) is even?
\end{problem}
\begin{solution}
	Let \(A:=\{x \in \mathbb{Z}:\exists y \in \mathbb{Z},a=yb+x\}\).
	Since \(a=0b+a\) we know \(a \in A\), so \(A \neq \emptyset\).
	By the definition of \(m\) we know \(\exists s,t \in \mathbb{Z},|t|=m,a=sb+t\).
	Then \(a=(s-1)b+(t+b),a=(s+1)b+(t-b)\). So by the definition of \(A\) we get \(t \pm b \in A\).
	Thus, by the definition of \(m\) we get \(|t \pm b| \geq |t|\).
	So we get \(||t|-|b|| \geq |t|\). Easily \(|t|-|b| < |t|\) since \(b \neq 0\), so we get \(|b|-|t| \geq |t|\), i.e., \(|t|\leq\frac{|b|}{2}\).

	Now take \(2 \nmid b\), we will prove the uniqueness.
	Assume there are two pairs \(s_1,t_1; s_2,t_2\) satisfy the given condition, then \(a=s_1 b + t_1=s_2 b + t_2\).
	Then we get \(b \mid s_1 b-s_2 b = t_2 - t_1\). Since \((s_1,t_1)\neq(s_2,t_2)\) we easily get \(t_1 \neq t_2\).
	So \(|b| \leq |t_1-t_2|\). Noting \(|t_1-t_2| \leq |t_1|+|t_2| \leq \frac{|b|}{2}+\frac{|b|}{2} = |b|\),
	we obtain \(|t_1|=|t_2|=\frac{|b|}{2}\).
	But \(2 \nmid b\), so \(\frac{|b|}{2}\notin \mathbb{Z}\), contradiction!

	Now we consider \(b \) is even.
	Take \(a \equiv \frac{b}{2}\mod b\), then \(a=kb + \frac{b}{2}\) for some \(k \in \mathbb{Z}\), and \(a=(k+1)b - \frac{b}{2}\).
	So there is exactly two pairs of \((s,t)\) satisfy the condition.
	When \(a \not \equiv \frac{b}{2} \mod b\), obviously \((s,t)\) is unique.
\end{solution}
\begin{problem}\label{pro:p6.3}
	Use Problem \ref{pro:p3.4} to prove the existence of the greatest common factor of any pair \((x,y) \in \mathbb{Z} \AND (x,y)\neq (0,0)\),
	and find an algorithm to get \(\gcd(x,y)\), and find \(\gcd(76501,9719)\) by your algorithm and Euckidean algorithm respectively.
\end{problem}
\begin{solution}
	Without loss of generality assume \(|x| \leq |y|\). If \(x=0\) then easily \(\gcd(x,y)=|y|\).
	Now assume \(|y| \geq |x| >0\). Now we prove \(\gcd(x,y)\) exists by contradiction, assume for some \(x,y \in \mathbb{Z},|x|\leq|y|\) there is \(\gcd(x,y)\) not exists.
	Let \(A:=\{x \in \mathbb{Z}:\exists y \in \mathbb{Z},|y| \geq |x|,\gcd(x,y) \text{not exists}\}\).
	Then \(A \neq \emptyset\). Let \(t = \min\{|x|:x \in A\}\). Then by the definition of \(A\) we know \(\exists s \in \mathbb{Z} \AND |s| \geq |t|\) such that \(\gcd(s,t)\) doesn't exist.
	Since we have proved \(\gcd(0,y)\) exists, we get \(t \neq 0\).
	From Problem \ref{pro:p3.4} we know there exists \(x,y \in \mathbb{Z}\) such that \(s=xt+y,|y| \leq \frac{|t|}{2}\).
	Consider the pair \((t,y)\), we know \(|y|< |t|\), so by the definition of \(t\) we get \(\gcd(t,y)\) exists.
	So \(\gcd(t,y)=\gcd(t,xt+y)=\gcd(s,t)\). Contradict to that \(\gcd(s,t)\) doesn't exist.
	So we get \(\forall(x,y) \in \mathbb{Z}^2 \AND (x,y)\neq (0,0),\gcd(x,y)\) exists.

	From above, we can get following algorithm to get \(\gcd(x,y)\):
	\lstinputlisting[style=Cstyle]{gcd.c}

	Now we use Euckidean algorithm to get \(\gcd(76501,9719)\).
	\[
		\begin{aligned}
			76501 & = 7  & \times & 9719 & + & 8468 \\
			9719  & = 1  & \times & 8468 & + & 1251 \\
			8468  & = 6  & \times & 1251 & + & 962  \\
			1251  & = 1  & \times & 962  & + & 289  \\
			962   & = 3  & \times & 289  & + & 95   \\
			289   & =3   & \times & 95   & + & 4    \\
			95    & = 23 & \times & 4    & + & 3    \\
			4     & = 1  & \times & 3    & + & 1    \\
			3     & = 3  & \times & 1    & + & 0
		\end{aligned}
	\]
	So \(\gcd(76501,9719)=1\).

	Now we use the new algorithm to get \(\gcd(76501,9719)\).
	\[
		\begin{aligned}
			76501 & = & 8   \times   & 9719    & - & 1251 \\
			9719  & = & (-8)  \times & (-1251) & - & 289  \\
			-1251 & = & 4   \times   & (-289)  & - & 95   \\
			-289  & = & 3   \times   & (-95)   & - & 4    \\
			-95   & = & 24  \times   & (-4)    & + & 1    \\
			-4    & = & (-4)  \times & 1       & + & 0
		\end{aligned}
	\]
	So \(\gcd(76501,9719)=1\).
\end{solution}
\begin{problem}\label{pro:p10.3}
	Assume \(f(x)=\sum_{k=0}^{n}a_k x^k \in \mathbb{Z}[x]\) and \(a_0,a_n \neq 0\).
	Prove that if a rational number \(\frac{p}{q},\gcd(p,q)=1\) is root of \(f\), then \(p \mid a_0,q \mid a_n\).
	Thus, \(\sqrt{2} \notin \mathbb{Q}\).
\end{problem}
\begin{solution}
	Since \(\frac{p}{q}\) is a root of \(f\), we get \(f(\frac{p}{q})=0\).
	So \(\sum_{k=0}^{n}a_k (\frac{p}{q})^k=0\).
	Multiple \(q^n\), we get \(\sum_{k=0}^{n}a_k p^k q^{n-k}=0\).
	Mod \(p\), we get \(p \mid 0 = \sum_{k=0}^{n}a_k p^k q^{n-k}\).
	For \(k>0\) we have \(p \mid a_k p^k q^{n-k}\), so \(p \mid \sum_{k=1}^{n}a_k p^k q^{n-k}\).
	So \(p \mid \sum_{k=0}^{n}a_k p^k q^{n-k}-\sum_{k=1}^{n}a_k p^k q^{n-k}=a_0q^n\).
	Since \(\gcd(p,q)=1\), easily \(p \mid a_0 q^n \iff p \mid a_0\).
	So we get \(p \mid a_0\).
	For the same reason easy to get \(q \mid a_n\).

	Consider \(f(x)=x^2-2 \in \mathbb{Z}[x]\). Easily \(f(\sqrt{2})=0\).
	So if \(\sqrt{2}=\frac{p}{q},\gcd(p,q)=1\), then we get \(p \mid 2,q \mid 1\).
	Without loss of generality assume \(q > 0\), then \(q=1\).
	Then \(\sqrt{2}=\pm 1 ,\pm 2\).
	But none of them is root of \(f\), contradiction!
\end{solution}

\end{document}
