%!Mode:: "TeX:UTF-8"
%!TEX encoding = UTF-8 Unicode
%!TEX TS-program = xelatex
\documentclass{ctexart}
\newif\ifpreface
\prefacetrue
\input{../../../global/all}
\begin{document}
\large
\setlength{\baselineskip}{1.2em}
\ifpreface
	\input{../../../global/preface}
	\newgeometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
\else
	\newgeometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
	\maketitle
\fi
%from_here_to_type
\begin{problem}
Assume \(\Omega \subset \mathbb{C}\) is a domain. Prove that \(f\) is meromorphic map over \(\Omega\) is equiv for \(\Omega\) as opensubset of \(\mathbb{C}\) and as Remian surface.
\end{problem}

\begin{solution}
	First we assume \(f:\Omega \to \mathbb{C}_{\infty}\) is holomorphic. Let \(T:=\{x \in \Omega:f(x)=\infty\}\).
	Now we prove \(f\) is meromorphic over \(\Omega\).
	Since \(\forall x \in T,f(x)=\infty\) and \(f\) is continous, we get \(\forall x \in T,\lim_{y \to x}f(y)=\infty\).
	Now we only need to prove every \(x \in T\) is isolated point. If not, we will prove \(f \equiv \infty\).
	Let \(V:=\{x \in \Omega:f(x)=\infty \wedge \exists x_n \in \Omega,x_n \neq x,x_n \to x,f(x_n)=\infty\} \neq \varnothing\).
	Easily \(V\) is closed in \(\Omega\), now we prove it's open, too.
	Assume \(x \in V\), and \(x_n \in \Omega,x_n \neq x,x_n \to x,f(x_n)=\infty\).
	Since \(f\) is holomorphic, we get \(\exists V:\infty \in V \subset \mathbb{C}_{\infty}\) is open, \(\exists U:x \in U \subset \Omega\) is open,
	such that \(g:=\phi \circ \res{f}{U} \circ \text{id}:U \to \mathbb{C}\) is holomorphic, where \(\phi(x)=\frac{1}{x}\).
	Then \(g(x)=g(x_n)=0\). So \(\res{g}{U}\equiv 0\). So we get \(\res{f}{U} \equiv 0\). So \(U \subset V\).
	So \(V\) is open in \(\Omega\). Since \(\Omega \) is connected, we get \(V=\Omega\).
	So \(f \equiv \infty\).

	Second we assume \(f:W \to \mathbb{C}\) is holomorphic, where \(W \subset \Omega\) is open,
	and \(\forall x \in T:=\Omega \setminus W,\lim_{y \to x}f(y)=\infty\), and \(x\) is isolated point.
	Now let \(h:\Omega \to \mathbb{C}_{\infty},\res{h}{W}=f,\res{h}{T}\equiv \infty\).
	We only need to prove \(h\) is holomorphic from \(\Omega\)(as Remian surface) to \(\mathbb{C}_{\infty}\).
	Only need to prove \( h\) is holomorphic on \(x \in T\). Let \(\phi:\mathbb{C}\setminus \{0\}\to \mathbb{C},x \mapsto \frac{1}{x}\).
	Let \(U \subset h^{-1}(\mathbb{C} \setminus \{0\}) \subset \Omega\) is a neibor of \(x\) and \(\forall y \in U \setminus \{x\},h(y)\neq \infty\).
	Now we prove \(g:=\phi \circ h \circ \text{id}:U \to \mathbb{C}\) is holomorphic.
	Easily \(h(z)= \frac{\psi(z)}{(z-x)^n}\) for some \(n \in \mathbb{N}^+\) and holomorphic map \(\psi\) where \(0 \notin \psi(U)\).
	So we get \(g(z)=\frac{1}{h(z)}=\frac{(z-x)^n}{\psi(z)}\) is holomorphic over \(U\).
\end{solution}

\begin{problem}
Let \(M\) is a Remian surface, \(f:M \to \mathbb{C}_{\infty}\) is holomorphic. Assume \(p \in M\).
Prove that \(\ord_p(f)\) is well-defined.
\end{problem}

\begin{solution}
	Assume \(U \subset M\) is openset and \(p \in U\), and \(\phi,\psi:U \to \mathbb{C}_{\infty}\) are holomorphic.
	Consider \(f_\phi:=f \circ \phi^{-1}:\phi(U)\to \mathbb{C}\) and \(f_\psi:=f \circ \psi^{-1}:\psi(U) \to \mathbb{C}\) are meromorphic.
	We only need prove \(f_\phi\) at \(\phi(p)\) and \(f_\psi\) at \(\psi(p)\) have the same ord.
	Since \(M\) is Remian surface we know \(\phi \circ \psi^{-1}:\psi(U)\to \phi(U)\) is holomorphic.
	Without loss of generality we can assume \(\phi(p)=\psi(p)=0\).
	Assume \(f_\phi(z)=z^nh(z)\), where \(h(z)\) is holomorphic near \(0\) and \(h(0)\neq 0\).
	Then \(f_\psi(z)=f_{\phi}\circ (\phi \circ \psi^{-1})(z)=\phi \circ \psi^{-1} (z)^n h(\phi \circ \psi^{-1}(z))\)
	Since \(\phi(p)=\psi(p)=0\) we get \(\phi \circ \psi^{-1}(0)=0\). So \(h(\phi \circ \psi^{-1}(0)) \neq 0\).
	And \(\lim_{z \to 0}\frac{1}{z}\phi \circ \psi^{-1}(z)\) exists.
	For the same reason we get \(\lim_{z \to 0}\frac{1}{z}\psi \circ \phi^{-1}(z)\) exists.
	So \(\lim_{z \to 0}\phi \circ \psi^{-1}(z)\neq 0\).
	So finally we get \(\ord_p(f)\) is well-defined.
\end{solution}

\begin{problem}
Assume \(p(z)\in \mathbb{C}[z]\) is a poly and not const.
Consider \(f:\mathbb{C}_{\infty}\to \mathbb{C}_{\infty},f(z)= \begin{cases}
	p(z)   & z \in \mathbb{C} \\
	\infty & z=\infty
\end{cases}\).
Prove that \(f\) is holomorphic.
\end{problem}

\begin{solution}
	Obviously for \(z \in \mathbb{C}\) we have \(f\) is holomorphic near \(z\). So we only need to prove \(f\) is holomorphic near \(\infty\).
	Let \(V \subset \mathbb{C}_{\infty}\) is a neibor of \(\infty\) and \(0 \notin V\).
	Since \(\deg p>0\), we get \(\lim_{z \to \infty}p(z)=\infty\).
	So \(\exists U \subset \mathbb{C}_{\infty}\) such that \(f(U)\subset V\). without loss of generality assume \(0 \notin U\).
	Now we only need to prove \(\phi \circ f \circ \phi\) is holomorphic at \(0\), where \(\phi(z)=\frac{1}{z}\).
	Assume \(f(z)=\sum_{i=0}^n a_i z^i\) and \(a_n \neq 0\), then \(\frac{1}{f(\frac{1}{z})}=\frac{z^n}{\sum_{i=0}^n a_i z^{n-i}}\).
	Since \(a_n \neq 0\) we get \(\frac{1}{f(\frac{1}{z})}\) is holomorphic near \(0\).
\end{solution}

\begin{problem}
Let \(\omega_1,\omega_1 \in \mathbb{C}^*\) and are \(\mathbb{R}\)-linear independent.
Let \(\Lambda\) is the addtive group generated by \(\omega_1,\omega_2\) and \(k \in \mathbb{N}^+,k \geq 3 \).
Prove that \(g(z)=\sum_{\omega \in \Lambda} \frac{1}{(z-\omega)^k}\) locally uniformly converge in \(\mathbb{C} \setminus \Lambda\).
And \(g(z)=g(z+\omega),\forall \omega \in \Lambda\).
\end{problem}

\begin{solution}
	Write \(\Lambda=\{z_n:n \in \mathbb{N}^+\}\), then we only need to prove \(\sum_{n=1}^{\infty} \frac{1}{(z-z_n)^k}\) locally uniformly converge in \(\mathbb{C} \setminus \Lambda\).
	Without loss of generality we can assume \(|z_n| \leq |z_{n+1}|,\forall n \in \mathbb{N}^+\).
	Easily we know \(\card(B(0,n)\cap \Lambda)=O(n^2),n \to \infty\).
	So we get \(|z_n|=O(\sqrt{n}),n \to \infty\).
	Assume \(M \subset \mathbb{C}\setminus L\) is cpt, now we need to prove the series converge uniformly in \(M\).
	Let \(\lambda:=d(M,\Lambda)>0\), then we get \(|z-z_n|>\lambda\).
	And \(|z_n-z| \geq |z_n|-|z| \geq |z_n|-\max\{|z|:z \in M\}=O(\sqrt{n}),n \to \infty\).
	So \(\exists N \in \mathbb{N}^+,t \in \mathbb{R}^+,\forall n>N,|z_n-z| \geq t \sqrt{n}\).
	For \(n \leq N\), we have \(|z_n-z| \geq \lambda\), without loss of generality assume \(t<\frac{\lambda}{\sqrt{N}}\), then \(|z_n-z| >t \sqrt{n}\), too.
	So finally we get \(\left|\frac{1}{(z_n-z)^k}\right| \leq \frac{t}{n^{ \frac{k}{2}}}, \forall z \in M\).
	Since \(\sum_{n \in \mathbb{N}^+} \frac{t}{n^{ \frac{k}{2}}}<\infty\), we get the series converge uniformly in \(M\).

	Now we prove \(g(z)=g(z+\omega)\). If \(z \in \Lambda\), then easily \(g(z)=\infty=g(z+\omega)\).
	Now we assume \(z \notin \Lambda\). Then we easily get \(|z-z_n|=O(\sqrt{n})\), so \(\sum_{n=1}^{\infty} \frac{1}{(z-z_n)^k}\) converge absolutely.
	So we can change the order of sum. Since \(\Lambda \to \Lambda,x \mapsto x+\omega\) is bijection, we get \(\exists \sigma:\mathbb{N}^+ \to \mathbb{N}^+\) is bijection
	and \(z_{\sigma(n)}=z_n-\omega\).
	So we get \(g(z+\omega)=\sum_{n=1}^{\infty} \frac{1}{(z-z_n+\omega)^k}=\sum_{n=1}^{\infty} \frac{1}{(z-z_{\sigma(n)})^k}=\sum_{n=1}^{\infty} \frac{1}{(z-z_n)^k}=g(z)\).
\end{solution}

\begin{problem}
Let \(\Lambda\) be same as above, let \(\wp(z):=\sum_{\omega \in \Lambda \setminus \{0\}} \left(\frac{1}{(z-\omega)^2} -\frac{1}{\omega^2}\right)+\frac{1}{z^2}\).
Prove this series converge locally uniformly in \(\mathbb{C} \setminus \Lambda\).
And \(\wp(z)=\wp(z+\omega),\forall \omega \in \Lambda\).
\end{problem}

\begin{solution}
	First we prove \(\wp(z)=\wp(z+\omega)\). If \(\omega=0\) or \(z \in \Lambda\) then it's obvious. Now we assume \(\omega \neq 0 \wedge z \notin \Lambda\).
	We write \(\Lambda\setminus \{0\}=\{z_n:n \in \mathbb{N}^+\}\) as above, then \(|z_n|=O(\sqrt{n})\).
	we first prove \(\sum_{n \in \mathbb{N}^+} \left(\frac{1}{(z-z_n)^2}-\frac{1}{z_n^2}\right)\) converge absolutely for \(z \notin \Lambda\).
	Since \(\frac{1}{(z-z_n)^2}-\frac{1}{z_n^2}=\frac{2z z_n-z^2}{(z-z_n)^2z_n^2}\) and \(|z_n|=O(\sqrt{n})\),
	we get \(\left|\frac{1}{(z-z_n)^2}-\frac{1}{z_n^2}\right|=O(\frac{1}{n^{ \frac{3}{2}} })\).
	So we get the series is absolutely converge.
	So we can change the order to sum.
	Write \(f(z,t)=\frac{1}{(z-t)^2}\) and \(g(t)=\begin{cases}
		\frac{1}{t^2} & t \neq 0 \\
		0             & t = 0
	\end{cases}\) for \(z \in \mathbb{C}\) and \(t \in \Lambda\). Then \(\wp(z)=\sum_{t \in \Lambda}f(z,t)-g(t)\).
	For \(t_1,t_2 \in \Lambda\), we define \(t_1 \sim t_2 \iff \frac{t_1-t_2}{\omega} \in \mathbb{Z}\).
	Then \(\sim\) is a equivalence relation of \(\Lambda\).
	We choose a class of reperentation element, write \(T\).
	Then \(\wp(z)=\sum_{t \in T}\sum_{n \in \mathbb{Z}}f(z,t+n \omega)-g(t+n \omega)\).
	And \(\wp(z+\omega)=\sum_{t \in T}\sum_{n \in \mathbb{Z}}f(z+\omega,t+n \omega)-g(t+n \omega)\).
	So to prove \(\wp(z)=\wp(z+\omega)\), we only need to prove \(\forall t \in T,\sum_{n \in \mathbb{Z}}f(z,t+n \omega)-g(t+n \omega)=\sum_{n \in \mathbb{Z}}f(z+\omega,t+n \omega)-g(t+n \omega)\).
	We can easily get \(|f(z,t+n \omega)|=O(frac{1}{n^2}),|g(t+n \omega)|=O(frac{1}{n^2})\), so we get \(\sum_{n in \mathbb{Z}}f(z,t+ n \omega)\) and \(\sum_{n \in \mathbb{Z}}g(t+n \omega)\) converge absolutely.
	So we get \(\sum_{n \in \mathbb{Z}}f(z,t+n \omega)-g(t+n \omega)=\sum_{n \in \mathbb{Z}}f(z,t+n \omega)-\sum_{n \in \mathbb{Z}}g(t+n \omega)\).
	For the same reason we get \(\sum_{n \in \mathbb{Z}} f(z+\omega,t+n \omega)-g(t+n \omega)=\sum_{n \in \mathbb{Z}}f(z+\omega,t+n \omega)-\sum_{n \in \mathbb{Z}}g(t+n \omega)\).
	So we only need to prvoe \(\sum_{n \in \mathbb{Z}}f(z,t+n \omega)=\sum_{n \in \mathbb{Z}}f(z+\omega,t+n \omega)\).
	Since \(f(z+\omega,t+n \omega)=f(z,t+(n-1)\omega)\) and \(n \mapsto n-1\) is bijection on \(\mathbb{Z}\), we get
	\(\sum_{n \in \mathbb{Z}}f(z+\omega,t+n \omega)=\sum_{n \in \mathbb{Z}}f(z,t+(n-1)\omega)=\sum_{n \in \mathbb{Z}}f(z,t+n \omega)\).
	So finally we get \(\wp(z)=\wp(z+\omega),\forall \omega \in \Lambda\).

	Now we prove the series converge locally uniformly in \(\mathbb{C}\setminus \Lambda\).
	Let \(M \subset\mathbb{C}\setminus \Lambda\) is cpt. Now we prove the series converge uniformly in \(M\).
	Only need to prove \(\sum_{n \in \mathbb{N}^+} \frac{2z z_n-z^2}{(z-z_n)^2 z_n^2}\) converge uniformly.
	Since \(|z|\) is bounded and \(|z_n|=O(\sqrt{n})\), we get \(\exists s \in \mathbb{R}^+,| 2z z_n-z^2| \leq s \sqrt{n}\).
	Since \(M\) is cpt we get \(d(M,\Lambda)>0\), so \(|z-z_n|\) has positive inf.
	So as above we get \(\exists t \in \mathbb{R}^+,|z-z_n| \geq t \sqrt{n}\).
	Without loss of generality we can assume \(t\) is little enough such that \(|z_n|\geq t \sqrt{n}\).
	So finally we get \(\left|\frac{2z z_n - z^2}{(z-z_n)^2 z_n^2}\right| \leq \frac{s \sqrt{n}}{t^4 n^2}=\frac{s}{t^4} n^{-\frac{3}{2}}\).
	Since \(\sum_{n \in \mathbb{N}^+} n^{-\frac{3}{2}}<\infty\), we get the series converge uniformly in \(M\).
\end{solution}
\end{document}
