%!Mode:: "TeX:UTF-8"
%!TEX encoding = UTF-8 Unicode
%!TEX TS-program = xelatex
\documentclass{ctexart}
\newif\ifpreface
%\prefacetrue
\input{../../../global/all}
\begin{document}
\large
\setlength{\baselineskip}{1.2em}
\ifpreface
    \input{../../../global/preface}
\newgeometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
\else
\newgeometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
\maketitle
\fi
%from_here_to_type
\begin{problem}
  Find all of irreducible complex reperesentation of \(D_4\). 
\end{problem}
\begin{solution}
  Write \(D_4=\left\langle \sigma,\tau:\sigma^4=\tau^2=1,\tau \sigma \tau = \sigma^{-1}\right\rangle \). 
  First we find all of conjugate class of \(D_4\), they are \(C_1=\{1\},C_2=\{\sigma,\sigma^3\},C_3=\{\sigma^2\},C_4=\{\tau,\sigma^2 \tau\},C_5=\{\sigma \tau,\sigma^3 \tau\}\). 
  Second we find all of \(1\)-dimetional reperesentation of \(D_4\). Only need to find all \(1\)-dimetional reperesentation of \(D_4/D_4'\). 
  Easily we get \(D_4'=\{\sigma^2,1\}\), so \(D_4/D_4'=\{D_4',D_4'\sigma,D_4'\tau,D_4'\sigma \tau\}\). 
  So \(D_4/D_4'\) has \(4\) different reperesentation, write \(\overline{\phi_0},\overline{\phi_1},\overline{\phi_2},\overline{\phi_3}\), where \(\overline{\phi_0}\) is main reperesentation. 
  And let \(\overline{\phi_1}(D_4'\sigma)=-1,\overline{\phi_1}(D_4'\tau)=1,\overline{\phi_2}(D_4'\sigma)=1,\overline{\phi_2}(D_4'\tau)=-1,\overline{\phi_3}(D_4'\sigma)=-1,\overline{\phi_3}(D_4'\tau)=-1\). 
  Then improve them to \(D_4\), we get \(\phi_0,\phi_1,\phi_2,\phi_3\), where \(\phi_0\) is main reperesentation, and 
  \(\phi_i(x)=\overline{\phi_i}(D_4'x)\). They are all of \(1\)-dimetional reperesentation of \(D_4\). 
  Now we find other irreducible reperesentation of \(D_4\). 
  Since \(|D_4|=8=1^2+1^2+1^2+1^2+2^2\) we get \(D_4\) has a \(2\)-dimetional irreducible reperesentation. 
  Consider \(\phi_4:D_4 \to M_2(\mathbb{C}),\sigma \mapsto \begin{pmatrix}
    0 & -1 \\
    1 & 0
  \end{pmatrix},\tau \mapsto \begin{pmatrix}
    -1 & 0 \\
    0 & 1 
  \end{pmatrix}\). 
  Obviously it's irreducible reperesentation of \(D_4\). 
  So all of irreducible reperesentation are \(\phi_0,\phi_1,\phi_2,\phi_3,\phi_4\). 
\end{solution}

\begin{problem}
  Find all irreducible reperesentation of \(Q\), the quaternions group. 
\end{problem}

\begin{solution}
  Write \(Q=\{\pm 1,\pm i,\pm j,\pm k\}\). Easily we get \(C_0=\{1\},C_1=\{- 1\},C_2=\{\pm i\},C_3=\{\pm j\},C_4=\{\pm k\}\) are conjugate class of \(Q\). 
  So \(Q\) has \(5\) different irreducible reperesentation. 
  Easily we know \(Q'=\{\pm 1\}\) and \(Q / Q'=\{Q',Q'i,Q'j,Q'k=Q'ij\}\). 
  Easily \(Q / Q'\) has \(4\) different \(1\)-dimetional reperesentation, write \(\overline{\phi_0},\overline{\phi_1},\overline{\phi_2},\overline{\phi_3}\), where \(\overline{\phi_0}\) is main reperesentation.
  And \(\overline{\phi_1}(Q'i)=-1,\overline{\phi_1}(Q'j)=1;\overline{\phi_2}(Q'i)=1,\overline{\phi_2}(Q'j)=-1;\overline{\phi_3}(Q'i)=\overline{\phi_3}(Q'j)=-1\). 
  Improve them we get \(\phi_0,\phi_1,\phi_2,\phi_3\), and \(\phi_0\) is main reperesentation, and 
  \(\phi_t(x)=\overline{\phi_t}(Q'x)\). 
  Since \(|Q|=8=1^2+1^2+1^2+1^2+2^2\), we get the last reperesentation is \(2\)-dimetional. 
  Consider \(\phi_4:Q \to M_2(\mathbb{C}),i \mapsto \begin{pmatrix}
    \mathrm{i} & 0 \\ 
    0 & -\mathrm{i}
  \end{pmatrix}, j \mapsto \begin{pmatrix}
    0 & \mathrm{i} \\
    \mathrm{i} & 0
  \end{pmatrix}\). 
  Easily we get \(\phi_4\) is irreducible, so \(\phi_t,t=0,\cdots,4\) are all irreducible reperesentation of \(Q\). 
\end{solution}

\begin{problem}
  Find all of irreducible reperesentation of \(A_4\). 
\end{problem}

\begin{solution}
  Obviously \(A_4'=K_4=\{(1 2)(3 4),(1 3)(2 4),(1 4)(2 3),(1)\}\). 
  And \(C_1=\{(1)\}, C_2=K_4,C_3=\{(1 2 3),(243),(134),(142)\}, C_4=\{(132),(124),(143),(234)\}\) are all of conjugate class of \(A_4\). 
  Easily \(A_4/K_4=\{(123)K_4,(132)K_4,K_4\}\). So it has \(3\) different irreducible \(1\)-dimetional reperesentation. 
  Write \(\overline{\phi_0},\overline{\phi_1},\overline{\phi_2}\), where \(\overline{\phi_0}\) is main reperesentation. 
  And \(\overline{\phi_1}((123)K_4)=\omega,\overline{\phi_2}((123)K_4)=\omega^2\). 
  Now improve then to \(A_4\), we get \(\phi_0,\phi_1,\phi_2\), where \(\phi_0\) is main reperesentation, and 
  \(\phi_t(x)=\overline{\phi_t}(xK4)\). 
  Sicne \(|A_4|=1^2+1^2+1^2+1^2+3^2\), we know the last irreducible reperesentation is \(3\)-dimetional. 
  Consider \(\phi_3:A_4 \to M_3(\mathbb{C})\), and 
  \[
    \phi_3((123))=\begin{pmatrix}
      -1 & -1 & -1 \\
      1 & 0 & 0 \\
      0 & 0 & 1
    \end{pmatrix}, \phi_3((124))=\begin{pmatrix}
      -1 & -1 & -1 \\
      0 & 1 & 0 \\
      1 & 0 & 0
    \end{pmatrix}
  \]
  Easily we get \(\phi_3\) is irreducible. 
  So all irreducible reperesentation of \(A_4\) are \(\phi_0,\phi_1,\phi_2,\phi_3\). 
\end{solution}
\end{document}
