%!Mode:: "TeX:UTF-8"
%!TEX encoding = UTF-8 Unicode
%!TEX TS-program = xelatex
\documentclass{ctexart}
\newif\ifpreface
%\prefacetrue
\input{../../../global/all}
\begin{document}
\large
\setlength{\baselineskip}{1.2em}
\ifpreface
    \input{../../../global/preface}
\newgeometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
\else
\newgeometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
\maketitle
\fi
%from_here_to_type
\begin{problem}
  \(R\) is a ring with identity element.
  If every non zero element in \(R\) is inversible, we call \(R\) is division ring.
  Prove: if \( D\) is a division ring, then \(M_n(D)\) is a monocycle.
\end{problem}
\begin{solution}
  Assume \(I\) is a non-zero two-sided ideal of \(M_n(D)\), now we only need to prove \(I=M_n(D)\). 
  Only need to prove \(E_{ij} \in I,\forall i,j\). 
  Since \(I \neq \{0\}\), assume \(A \in I\) and \(A_{st} \neq 0\). 
  Then \(\forall i,j,E_{is}AE_{tj} \in I\). i.e., \(a_{st} E_{ij} \in I\). 
  So \(a_{st}^{-1}I_n a_{st}E_{ij} \in I\), i.e., \(E_{ij} \in I\). 
  So \(I = M_n(D)\). 
\end{solution}

\begin{problem}
  \(V\) is right module of division ring \(D\), let \(\hom_D(V,V)\) is the set of all module isomorphic of \(V\). 
  Given \(\dim_DV=n\), prove that \(\hom_D(V,V) \cong M_n(D)\). 
\end{problem}

\begin{solution}
  Assume \(\{a_1,\cdots,a_n\} \) is a maximal linearly indenpendent set of \(V\). 
  First we prove \(\forall x \in V,\exists ! d_1,\cdots,d_n \in D\) such that \(x = \sum_{k=1}^{n} d_ka_k\). 
  
  Existence: Since \(A\) is maximal linearly indenpendent set, we have \(A \cup \{ x \}\) is not linearly indenpendent. 
  So \(\exists t_1,\cdots,t_n,t \in D\) such that \(\sum_{k=1}^{n} t_ka_k +tx =0\) and \(t_1,\cdots,t_n,t\) are not all \(0\). 
  If \(t=0\),  then we get \(a_1,\cdots,a_n\) are not linearly indenpendent, contradiction! 
  So \(t \neq 0\). Since \(D\) is division ring, we get \(\exists w \in D\) such that \(tw=wt =1\). 
  Let \(d_k=-wt_k,k=1,\cdots,n\), then \(\sum_{k=1}^{n} d_ka_k=\sum_{k=1}^{n}-wd_ka_k=wtx=x \).

  Uniqueness: If \(x=\sum_{k=1}^{n} d_ka_k=\sum_{k=1}^{n} t_k a_k\), then \(\sum_{k=1}^{n} (d_k-t_k)a_k=0\). 
  Since \(a_k,k=1,\cdots,n\) is linearly indenpendent, we get \(d_k-t_k=0,k=1,\cdots,n\). 
  So the form is unique. 

  Now let \(f_j:V \to D,\sum_{k=1}^{n} d_ka_k \mapsto d_j\), for \(j=1,\cdots,n\). Then \(f_k\) is well-defined. 
  Let \(F:\hom_D(V,V) \to M_n(D), F(\phi)_{ij}:=f_i(\phi(a_j))\). Now we prove \(F\) is isomorphic. 

  Since  \(\phi(\sum_{k=1}^{n} d_ka_k)=\sum_{k=1}^{n} d_k \phi(a_k)\), so 
  \(\phi(\sum_{k=1}^{n} d_ka_k)_i=\sum_{k=1}^{n} d_k F(\phi)_{ik}\). 
  So \(\phi\) can be reperesented by \(F(\phi)\), so \(F\) is injection. 

  For \(A \in M_n (D)\), assume \(A=(a_{ij})\). Let \(\phi(\sum_{k=1}^{n} d_ka_k)_i:=\sum_{k=1}^{n} d_ka_{ik}\). 
  Easily we get \(\phi \in \hom_D(V,V)\). And \(F(\phi)=A\). So \(F\) is surjective. 

  Easily \(F(\phi \psi)_{ij}=f_i(\phi \psi a_j)=f_i(\phi \sum_{k=1}^{n} f_k(\psi a_j)a_k)=\sum_{k=1}^{n} F(\phi)_{ik}F(\psi)_{kj}\). 
  So \(F(\phi \psi)=F(\phi) F(\psi)\). 
  And obviously \(F(a \phi+ b \psi)=aF(\phi)+b F(\psi)\). 

  So all in all we get \(F\) is a isomorphic. 
\end{solution}
\end{document}
